%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
% Project Highlights variant: Embodied Intelligence.
% Focus: real-world perception, motion priors, and interaction skills for embodied agents.
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\begin{rSection}{Project Highlights}

    {\bf Real-World 3D Perception and Reconstruction.} Embodied agents need faithful 3D perception of the world they act in. I have built accessible infrastructure to capture and reconstruct real-world humans and scenes: \href{https://github.com/zju3dv/EasyMocap}{EasyMocap} (4.7K+ GitHub stars) recovers 3D human motion from sparse multi-camera rigs and in-the-wild internet videos, and \href{https://github.com/zju3dv/LoG}{LoG} (770+ GitHub stars) delivers real-time interactive photorealistic 3D scene reconstruction. Together they provide the geometry, appearance, and motion priors that grounded embodied policies depend on, and they turn observations of humans into scalable behavior data for imitation learning.

    {\bf Motion Priors and Interaction Skills.} A large portion of embodied skills reduces to producing physically plausible motion under multimodal conditions. I have built industrial-scale motion generation systems around this: \href{https://github.com/Tencent-Hunyuan/HY-Motion-1.0}{HY-Motion 1.0} (2.5K+ GitHub stars) is a flow-matching text-to-motion model that I drove from research to product, deployed in Tencent's Hunyuan 3D Studio and Honor of Kings: World for AI NPC gameplay. On top of it, I work on interactive motion skills such as \href{https://zju3dv.github.io/ready_to_react/}{Ready-to-React} for online two-character reaction policies, and close-range multi-person interaction reconstruction (SIGGRAPH Asia 2023), giving embodied agents a library of reusable motion priors and reactive skills.

    {\bf From Simulation to Product Deployment.} I care about closing the loop between research prototypes and real embodied systems. My work has been integrated into shipping products including Tencent's Hunyuan 3D Studio and the AI NPC pipeline in Honor of Kings: World, and I co-founded Image Derivative Inc.\ to industrialize digital human capture and animation. This experience covers the full stack of embodied delivery: data infrastructure, real-time inference on constrained platforms, engine-side integration, and iteration with product feedback.

\end{rSection}
